---
title: Are Canadians living with their common-law partners?
author: Prinsa Gandhi
date: October 19, 2020
output: pdf_document
latex_engine: xelatex
 
abstract: This paper will be analyzing the the Canadian General Social Survey of 2017 which had the theme of *The Family*. I will be analyzing the factors that influence whether respondents were currently living with their common-law partner at the time of the survey, specifically, the response variable *lives_with_partner*. After cleaning the GSS dataset and exploratory data analysis, I performed variable selection to determine important variables for the response variable. My final model is quite interesting, and the important factors which were key in predicting whether people live with their common-law partner are very important for decision making and understanding the evolving theme of families. 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

### The code and data supporting this analysis is avaliable at: 
[github](https://github.com/username1-p/Are-Canadians-living-with-their-common-law-partners-)
https://github.com/username1-p/Are-Canadians-living-with-their-common-law-partners-



## Introduction


The role of the family is an important area of study for quite some time now. The importance and impacts of a family in child development and mental and emotional health are a key area of interest. The studies of families in Canada help government officials understand the evolving Canadian family and make important decisions. The GSS survey of 2017 focussed on the family, and there are many important variables and results that can be understood from this study. A key statistic that I noticed while analyzing the data is that about 89.9% of respondents answered "No" to the survey question asking if the respondent currently lives with their common-law partner, and about 10% responded "Yes". That is an astonishing statistic, and the goal of this paper will be to analyze and try to model this response variable of “lives_with_partner”. This will help Canadian government officials determine if more social service programs are needed, observe the new way of family life, and also use this information in further researching the evolving family. The concept of social isolation is a key area of study, and I will try to help model the reasons behind this behavior of social isolation. The government officials may decide if more social support programs are need, or if more research is needed in the impacts of social isolation, and run programs to help promote the need for emotional connection between humans. The important question of whether couples are separately will be analyzed, and the model will try to determine important predictors for this question.



```{r, ECHO=F, results='hide', include=FALSE}
#some packages first
rm(list = ls())

library(tidyverse)
library(nnet)
library(rms)
library(dplyr)
library(glmnet)
library(ggplot2)
require(gridExtra)
                                                
#install.packages("imputeMissings")
library(imputeMissings)
#install.packages("RSQLite")
library(RSQLite)
#install.packages('kableExtra')
library(kableExtra)

#install.packages("gtsummary")
library(gtsummary)
library(survey)
```

```{r, echo=FALSE, results='hide', include=FALSE}
mydata <- read.csv("gss.csv")
#check missing values
is.na(mydata)
colSums(is.na(mydata))
((colSums(is.na(mydata)))/20602)*100

#remove major missing variables 80-90% data missing 
mydata <- mydata[-c(4,6,7,9,10,16,18,25,26,36,50,51,52,55,65,66,
                    67,68,69,70,71,72,73,74,75,76,79)]


#impute missing values
newdata <- impute(mydata,method = "median/mode")
colSums(is.na(newdata))

lapply(mydata[], unique)

colSums(is.na(mydata))


test <- newdata[sample(seq_len(nrow(newdata)), size = 6180),]
train <- newdata[!newdata$caseid %in% test$caseid,]

#proportions of response variable
countno <-  which(newdata$lives_with_partner=="No")
length(countno)
length(countno)/20602

countyes <-  which(newdata$lives_with_partner=="Yes")
length(countyes)
length(countyes)/20602


```
## Data

   In this analysis, I will be using data collected by Statistics Canada as part of its General Social Survey program. This program started in 1985, and consists of surveys in the ten Canadian provinces. The regular collection of this data helps address important issues. According to the social and aboriginal statistics division, which is part of Statistics Canada, the objectives of the GSS are to collect data on social trends and to provide information on social policy issues. The key topic of the 2017 social survey is “Family”. The data collection revolved around family life, and questions involving the family. The frequency of this topic is every 5 years. I selected the topic of the family, as part of the GSS, because this seemed to be a very important topic of interest for me. This data is a very relevant dataset to analyze in 2020 because COVID-19 has caused a majority of Canadians to follow social isolation guidelines, and stay at home. As public health guidelines advice to stay within one’s own social bubble, and immediate family, the question of families in Canada is important to analyze. Do many Canadians have a family they live with? Are Canadians living with their common-law partner? During COVID-19, there have been many concerns regarding mental health, loneliness due to social isolation. It is very important people have a family during this time which is why I chose the analyze the 2017 Family GSS.

   I found this data from the UofT Chass website.  This data had target population of all non-institutionalized persons 15 years of age or older, living in Canada’s 10 provinces. The survey was a sample survey and it had a cross-sectional design. The sampling frame was a combination of landline and mobile telephone numbers accessed from the census and other sources within Statistics Canada’s frame. Statistics Canada also used the Address Register to match the list of telephone numbers to their addresses.  The frame has telephone numbers that were associated with the same address. Thus, the frame was unique households given by their unique telephone numbers for the household. The frame population was the units covered by this sampling frame. The survey was voluntary, and the response rate was 52.4% (Statistics Canada). The target sample size was 20,000, and respondents was 20,602.  Thus, the sampled population was 20602, out of Canada’s total 2017 population of 36,708,083(Statistics Canada). This data was collected with stratification first, and then simple random sampling without replacement within a stratum. The 10 provinces were divided into strata, and they were further stratified at the CMA level which is the census metropolitan area level, for a total of 27 strata. There were minimum sample sizes per province, to ensure variability within the stratum, such that they can equally represent all the 10 provinces. The random households were chosen in the stratum for the SRSWOR. According to Statistics Canada, a 43,000 sample was used. In the 43,000, about 34,000 letters were sent to households, the goal was a completion of 20,000 surveys. As mentioned above, there were 20,602 respondents. 
   
   The actual survey methods were through computer assisted telephone interviews, and responses were entered directly into the computer program while the interview progressed. It was rare the key variables such as age, or sex were missing and they were imputed by estimating household information, or details from the interview. Imputation was rarely used, but used in only some key cases where it was necessary such as key variables and where possible. Missing values for questions are denoted by “na” as seen in the dataset. 
   
   In the appendix (Figure 1), I have presented a sample of 6 surveys done by individuals, seen by their unique case ID. The data collection has important variables such as age, sex, age when individual had their first child, place of birth, province, marital status, self rated health and mental health, family income, future children intention, age difference respondent. These variables are important for this study and to understand my response variable regarding whether the respondent lives with their partner. These variables can be used for general statistics regarding martial status, average number of children, etc... In my model, I perform model selection and obtain the variables age, marital status, feelings in life, children in household, whether place of birth is Canada, and family income to predict the response lives with partner. These variables are self explanatory, and the feelings in life uses a scale of 0-10 to describe how a respondent feels about life in general. There are many variables that are similar such as total children, place of birth of province, self rated health, future children intention, however, I used various model selection techniques to obtain my model and I removed predictors that would have a substantial number of missing values from my model because I did not want to have an incorrect analysis with “NA” values and my imputations would underestimate variance. 


   In terms of this survey in general, I like the way the stratification and SRSWOR was done to ensure a whole population is represented. The method of conducting the survey had many pros and cons. I liked the telephone and computer aspect, because I believe an interviewer reading the questions would allow the survey to be serous and without any confusion, and entering answers on a computer screen allows respondents to feel a sense of anonymity as well, which is important for accurate answers. The survey was conducted very well. A con about this survey is that many respondents chose to answer many questions with “NA” such as do not want to answer. This led to a very complicated data analysis, and I wonder if the respondents felt uncomfortable giving answers to some multiple-choice questions because of the wording of the questions. The survey includes many important aspects of family life, which allows for rich data and analysis on numerous variables. Overall, I think this was a very nicely conducted survey and there is a lot of rich data present. I think “NA” values are very common in surveys since people may avoid questions, but it still allows for analysis and comprehensive results. 



## Exploratory Data Analysis

Figure 1
```{r, echo=FALSE}
newdata %>% 
  ggplot(aes(y=lives_with_partner, x = age)) +
  geom_boxplot() +ggtitle("Age vs. Living with Partner") +labs(y= "Lives with partner", x = "Age")



```
In Figure 1, I examine the impacts of age on the decision of Canadians to live with their common law partner. The results are quite interesting, as seen in the box plot. The older age group of 40-70 answered no, while the age group of 35-55 answered yes. There seems to be correlation between age and living with a partner, so I will analyze this further in my model. I also have many questions wondering if an older age group prefers to live alone, and what factors could influence this decision.  

Figure 2

```{r, echo=FALSE}

plot1<-newdata %>% 
  ggplot(aes(y=feelings_life, x = age)) +
  geom_point() +ggtitle("Age and Feelings in life")
plot1




```

As in figure 2, I do not see a correlation between age, and feelings in life in general. All ages seem to have experiencing a wide range of feeling levels from 0-10. 

Figure 3
```{r, echo=FALSE}

plot2<-newdata %>% 
  ggplot(aes(y=marital_status, x = age)) +
  geom_boxplot() +ggtitle("Age vs Marital Status")


plot3<-newdata %>% 
  ggplot(aes(y=living_arrangement, x = age)) +
  geom_boxplot() +ggtitle("Age vs Living Arrangements")


require(gridExtra)
grid.arrange(plot2, plot3, ncol=2)



```
In figure 3, the data visualization is very interesting. An older age group seems to be divorced, thus, this could be a reason why an older age group lives alone. The near 80 age group is mostly widowed. The 25-45 age group is married or living with a common-law partner, and the age group 40-60 is either married or separated. In living arrangements, younger age groups are living with parents. The 55-75 age group seems to be living alone. The age group of 40-60 seems to be living with spouses only, spouse and children, and importantly, I do not see a majority of this age group living alone. 

Figure 4

```{r,  echo=FALSE}
plot9<-newdata %>% 
  ggplot(aes(x=age, y= age_at_first_birth)) +
  geom_point() +ggtitle("Age vs Age at first birth")
plot9

```

In figure 4, I see that the younger age group has a older age at first birth which seems to be around 28. In the older age groups(60+), I see the age at first birth seems to be younger than 25. It seems new famillies are delaying having children, and older couples had children at a younger age. Now, in terms of living with a partner, the age of first birth and living with children might be an important predictor for my response variable lives with partner. 

## Model
```{r, echo=FALSE, include=FALSE}
#please uncomment to run these codes. They were part of my analysis to find my #model, but i commented out after obtaining my final model, since it takes lots #of time to run while compiling pdf output

#modelnew <- glm(as.factor(lives_with_partner) ~ ., newdata, family="binomial")
#doesnt converge!

#model3 is model that worked which also converged

#model3<- glm(as.factor(lives_with_partner) ~ 
 #                 
  #                age + age_first_child  +age_at_first_birth + feelings_life+
   #               sex+
    #              
     #             place_birth_canada           +
      #            place_birth_province      +  province     + marital_status+
       #        aboriginal+ vis_minority + citizenship_status +education+own_rent
     #         +partner_vis_minority  
      #       
       #      + as.factor(self_rated_mental_health) +
        #       ever_given_birth + ever_fathered_child
            #+as.factor(children_in_household)
         #   +number_total_children_intention + has_grandchildren
          #  +grandparents_still_living
            #+ever_married
           # +number_marriages + future_children_intention 
                  
            #      , train, family="binomial")


#summary(model3)

#aic selection
#aic <- step(model3, trace = 1, k=2)

#BIC SELECTION
#n <- nrow(train)
#bic <- step(model3, trace = 1, k = log(n), direction = "both") 
#bic<-attr(terms(bic), "term.labels")   
#bic

#modelselect <- glm(as.factor(lives_with_partner) ~ age_first_child + feelings_life + 
 #                    marital_status + aboriginal + partner_vis_minority, 
  #                 train[-c(1),], family="binomial"
                     
#)

#trying to get good predictors, i will add what i believe to be important now, compare with anova
#anova(modelselect, test="Chisq")

#modelcompare1 <- glm(as.factor(lives_with_partner) ~ age+age_first_child + feelings_life + 
        #             marital_status + aboriginal + partner_vis_minority, 
         #          train[-c(1),], family="binomial"
                   
#)

#anova(modelselect, modelcompare1, test="LRT")

#age is added

#modelcompare1 <- glm(as.factor(lives_with_partner) ~ age+age_first_child + feelings_life + 
          #             marital_status + aboriginal + partner_vis_minority, 
           #          train[-c(1),], family="binomial"
                     
#)

#modelcompare2 <- glm(as.factor(lives_with_partner) ~ age+age_first_child + feelings_life + 
 #                      marital_status + aboriginal + partner_vis_minority + #total_children +sex
  #                   +place_birth_canada +province , 
   #                  train[-c(1),], family="binomial"
                     
#)
#modelcompare3 <- glm(as.factor(lives_with_partner) ~ age+age_first_child + feelings_life + 
 #                      marital_status + aboriginal + partner_vis_minority + total_children +sex
#                     +place_birth_canada +province +living_arrangement #+pop_center+vis_minority
 #                    +average_hours_worked #+self_rated_health+self_rated_mental_health 
 #                    +income_family+children_in_household, 
  #                   train[-c(1),], family="binomial"
                     
#)

#summary(modelcompare3)

#anova(modelcompare3, test="Chisq")

#anova(modelcompare2, modelcompare3, test="LRT")


#health and mental health!!income_family!!children in household!!
#total chldren add, sex add, place_birth_canada, province, LIVING ARRANGMENT MUST ADD, avg hours worked!!
#pop_center, vis_minority unsure...



#modellogit <- glm(as.factor(lives_with_partner) ~ age+age_first_child + feelings_life + 
 #                      marital_status + aboriginal  +sex
  #                   +place_birth_canada  +living_arrangement 
   #                  +average_hours_worked +self_rated_health+self_rated_mental_health 
 #                    +income_family+children_in_household, 
   #                  train[-c(1),], family="binomial"
                     
#)

#summary(modellogit)



#aic selection
#aic <- step(modellogit, trace = 1, k=2)

#BIC SELECTION
#n <- nrow(train)
#bic <- step(modellogit, trace = 1, k = log(n), direction = "both") 
#bic<-attr(terms(bic), "term.labels")   
#bic


modelfinal <- glm(as.factor(lives_with_partner) ~ age+ marital_status 
                    
                    + feelings_life  +children_in_household +place_birth_canada
                  +income_family ,
                    
                  
                  train[-c(1),], family="binomial")
                  

plot(modelfinal)

summary(modelfinal)


#elastic net
fit = glmnet(x=model.matrix(~ ., data=train[, -c(1)]), y=train$lives_with_partner, family = "binomial")
plot(fit, xvar = "dev", label = TRUE)


cvfit = cv.glmnet(x=model.matrix(~ ., data=train[,  -c(1)]), 
                  y=train$lives_with_partner, family = "binomial", type.measure = "class")


plot(cvfit)

cvfit$lambda.min

cvfit$lambda.1se

coef(cvfit, s = "lambda.min")
coef(cvfit, s = "lambda.1se")


```

# Methods

   The first step was to clean the GSS data, using the GSS Cleaning R codes. After cleaning, there were about 20602 observations of 81 variables in the original dataset. My first steps were to perform EDA which is shown above, and to try to determine correlations and important variables that I could see for my response variable “lives with partner”. I checked for missing values in the R code, and realized there were numerous missing values, which is something that happens in survey data. I could not perform complete case analysis, since that would mean every single datapoint would be deleted. Instead, I check for predictors with a huge amount of missing values, which I believe would make the data unreliable and it cannot contribute much to my model. If I were to impute, there would be an underestimated variance. Thus, I removed the predictors “age youngest child under 6” where 89% of data was missing, “age start relationship” where 90% was missing, “partner sex” where 90% was missing, and more which is shown in the appendix. I removed predictors which had more than 55% missing values. Upon further analysis, I realized each data point has a missing value. I did not want to create the “NA” as an additional factor level for my categorical variables, and it did not make sense to have “NA” in numerical variables since it would not allow my model to work. Thus, I decided to use mean, median and mode  imputation. For my numerical values, I decided to use mean instead of the “NA” values and for categorical, I imputed the mode for these variables. I decided to impute this way, because this would not change the sample mean of variables. I knew this would underestimate variance, so I took that into account in my final model. This imputation technique is a quick technique that allowed me to still obtain the correct predictors based on numerous analysis techniques.  

   The data points were all independent and my response variable is “yes/no” categorical, which satisfied an assumption of logistic regression. My response variable assumes a binomial distribution. Thus, I decided to use a generalized linear model, which was a logistic regression model. 
   
   First, I split my data into train and test sets. I decided to perform GLM model selection methods, such as AIC, BIC, and LASSO model selection to try to determine the best predictors. I believe these methods can perform well for interpretation, and give a nice prediction model as well. I did not find high collinearity between the final predictors that I chose for my model. My first model used all predictors available, which did not converge. Thus, I decided to try ANOVA tests to try to add predictors one by one, and determine which predictor was significant. I also tried to remove the predictors that were causing complete separation in my logistic model. After this initial step, I performed AIC and BIC selection. My AIC selection yielded the variables age_first_child, feelings_life, marital_status, aboriginal, partner_vis_minorty. The BIC selection yielded marital_status. I decided to add all the predictors, and removed predictors which were causing collinearity, complete separation, and I added predictors which I felt must be important such as age which I knew was important from EDA. I performed AIC/BIC selection on these new models, and I tried ANOVA tests to compare models. 
   
   My final model result was:

 lives_with_partner ~ age+ marital_status   + feelings_life        +children_in_household +place_birth_canada  +income_family 
 
   These were all significant predictors, and I also performed model diagnostics to check this model further. My model converges with no errors. The residuals vs Leverage plot had some high leverage points, but I decided not to remove them, since I felt that they didn’t affect the model too much. I felt cooks distance points did not have a large influence. While looking at residual plots, I’m seeing few residuals as well. 

   I have also considered some alternate models. Firstly, because this survey was conducted by using SRSWOR, I decided to use the SVYGLM function on this identical model. I got the same coefficient values for all my predictors, and my standard error of the coefficients drastically reduced because of the finite population correction, which makes me believe my model is more accurate than I thought when I was using GLM. For this model, I used n=14422, which was the number of observations of my response variable. I used N=37000, because this was a trial model, and I wanted to see the impact of the population correction. 

   Furthermore, I know this survey was conducted by creating 27 different stratum and then performing SRSWOR from these strata to get a data that is representative of the entire population. In this dataset, I did not see a datapoint representing which strata the point was from, and the sample size of each stratum. I believe with further time and research, upon obtaining this information, if I were to create a model with SVYGLM based on stratified sampling, there would be an even further decrease in my standard error, and my p-values would show the points are even more significant, as seen in the SRSWOR model. 



## Results

After obtaining my logistic regression model, this is a table of key coefficients for my model and important summary statistics. 

Table 1

```{r, echo=FALSE, warning=FALSE}

summary(modelfinal)





```
   As seen above in table 1, there are coefficients shown for the predictors. For categorical variables, the category not shown in the table has coefficient 0, and is the baseline category. For example, marital status:divorced is the baseline category for marital status variable. An important note is that the standard error seems extremely high because I am using a GLM and this did not account for the population correction. This will be explained in the discussions section. As seen in the table, the p-values show that my coefficients are significant, and again, they become much more significant when looked at in the population  corrected model using SVYGLM function. 



   In logistic regression,interpretation using odds ratio is done. Thus, the odds ratio for my predictors are given in table 2. This table has 95% confidence intervals, and p-values shown below.   

   Table 2
```{r, echo=FALSE, warning=FALSE, message=FALSE}

tbl_regression(modelfinal, exponentiate = TRUE)

```

   The resulting regression formula is: 
Lives_with_partner = -5.95109117 + 0.01133991age + 10.65136076marital_statusLiving common-law +     -17.84328330marital_statusMarried + 1.50703824marital_statusSeparated + 0.06761685 marital_statusSingle, never married + -0.64014053 marital_statusWidowed + -0.05089664 feelings_life + 1.17518659 children_in_householdOne child + 1.94781349 children_in_householdThree or more children + 0.47604589 children_in_householdTwo children  + 
-0.86133357 place_birth_canadaBorn outside Canada + -3.26613485 place_birth_canadaDon't know + 0.11538115 income_family$125,000 and more + -1.10432088 income_family$25,000 to $49,999 + -0.88196386 income_family$50,000 to $74,999 + -0.04930344income_family$75,000 to $99,999+ -1.64121821 income_familyLess than $25,000   

   Figure 5
```{r, echo=FALSE}

res.dev <- residuals(modelfinal, type = "deviance")
plot(res.dev)+ title("Residuals Plot")

```
   
   The accuracy of my model can be seen in this residuals plot, where most residuals are near 0, which is a good sign. There are some residuals with magnitudes greater than 2 on either side of 0, however, they are not extremely high magnitude residuals and these points do not seem to be outliers. 
   
   I have also conducted some additional diagnostic tests shown below. They are all based off of my final model.  


Figure 6-Diagnostic Plots  
```{r, echo=FALSE, fig.height = 3, fig.width = 3, fig.align = "center"}
plot(modelfinal)


```


   Above, I have included some model diagnostics plots.In the residuals vs. fitted plot, most points are around 0(and if zoomed in they would be seen to be bouncing around 0), and I can see some outliers, which I did not remove, to allow for some variance in the model and avoid overfitting. The Normal QQ-plot is not a 45 degree line, as it should not be, since I assume a binomial distribution, and I can see a logit pattern as well in this plot. 
     
   The scale location plot shows residuals spread around 0(if zoomed in, can see more clearly), and I see quite a bit of outliers. I still chose not to remove these outliers because I already performed some imputation in the data, and I did not want to risk overfitting. 
   
   The residuals vs. leverage plot shows some Cook's distance points. I see most points are within Cook's distance, and a few points outside of Cook's distance. The points only look clustered because the plot is scaled for the y-axis, however, overall, I think most points are within Cook's distance, which is an important criteria in model diagnostics.  




## Discussion

   The analysis of the GSS-Family dataset of 2017 yielded many interesting results. Based on the analysis conducted I found that many Canadians prefer to live alone, and some major predictors for this behaviour are age, marital status, feelings for life, the number of children in a household, if birth place is Canada, and family income. These results shown in the results section can really help Canadian researchers and government officials make decisions. The effect of marital status of living common-in-law versus being divorced is 10.99.
The effect of being married is -18.18 times. The effect of being widowed is -17 times. The effect of having one child is 1.28 times versus having no child. The effect of family income less than $25,000 is -2.15. A one unit change in age, results in a 0.019 change in the log of the odds. A one unit change in feelings for life results in a 0.18 change in the log of the odds. I have odds ratios given for my variables, however, since my predictors have more than 2 categories the interpretation is a bit more complex. The odds ratio for marital status of separated  is the odds of living with partner for separated over odds of living with partner for divorced, which is 2.71. The odds ratio for children in a household-one child is the odds of living with partner for for one child over odds of living with partner with no child, which is 3.58. These were the most important according to me, similar interpretation is used for the rest of the variables. 


The standard error of marital status widowed is huge of 2103, but this decreases when I take into account the finite population correction to 0.52. The AIC is 309.36 and the residual deviance is 273.36. The probabilities for the z-values of the predictors are quite small, which shows they are significant predictors.

The diagnostic tests are already discussed above with the diagnostic plots. 
   
   
   It is shown in research that family can really impact individuals and children, thus, if a majority of the population prefers to live alone it may lead to consequences and health issues for individuals. During COVID-19, individuals are stuck at home, and thus, living with family is important for individuals to avoid complete social isolation. My results show that feelings for life and family income are key predictors for individuals to live alone, so the government may want to introduce social service programs or initiatives that help Canadians maintain a positive outlook for their life. A lower family income may be a high-risk group, so they may need more support to avoid wanting to isolate from each other. Additionally, higher age group individuals are preferring to live alone, thus, money can be spent to help Canadian researchers determine the reasons behind this particular age group living alone. 


# Weaknesses

   I think a shortcoming of this survey is that individuals decided to avoid answering numerous questions, and this can lead to a false analysis. I adjusted for the missing value, but if they were more complete, my analysis might have found different predictors for individuals preferring to live alone. Additionally, with further resources, I can get more correct results using the stratified sampling approach from the SVYGLM function. I believe some level of error is introduced because of my imputation methods, and this may cause error in AIC/BIC selection, however, I already removed the predictors with high proportion of missing values, thus, the error should not be too high, and analysis results should still be accurate.  
   
   Here is a my results when I used SVYGLM, under the assumption that this data was collected with only SRSWOR. This provides me with more accurate standard errors of the coefficients and p-values.  
   
   
```{r, echo=FALSE}
   
## Using the Survey Library

## Survey Estimation for Logistic Regression- simple random sampling
n=length(train$lives_with_partner)
N1=37000
#N 37000 is the target population
fpc.srs = rep(N1, n)

design <- svydesign(id=~1, data=train, fpc=fpc.srs)

mysvyglm <- svyglm(as.factor(lives_with_partner) ~ age+ marital_status 
                   
                   + feelings_life  +children_in_household +place_birth_canada
                   +income_family
             
                   , 
                   design, family="binomial")
summary(mysvyglm)
   
```
   
   Furthermore, I chose a GLM because this model is great for statistical interpretation and inference. However, if the goal is further predictive accuracy, there can be other machine learning methods such as random forest, bagging, boosting, etc. and these methods might allow for different predictors that are more accurate. Additionally, I used mean and mode imputation, but there are numerous complex imputation methods available which are very complex and can reduce the problems of underestimating variance and reduce bias as well. This can be very helpful for a deeper analysis, if given more time, I would try the different imputation methods and compare the results. 

# Next Steps

   The next steps would be a by using this model on the stratification model as mentioned above. If the results are quite different, I would try to perform model selection again based on the results. I believe the government officials should use these results and promote initiatives which show the importance of positivity in life, and also the importance of relationships and family. There are numerous areas of discussion based on this survey, and numerous areas that can be further analyzed to understand decisions. My other next steps would be to analyze the other important variables such as if individuals are satisfied with the time with their children, future children intentions, self rated health, etc.. because all of these variables are important to understand the Canadian family as a whole and see the relationship between these important variables. 
   
   There can be a follow-up survey of these same individuals that are currently 20-40 years of age, and see the results after about 20 years when these individuals are older and see if these same individuals who live with their common-law partners are living alone later in life. This study would be important because it is seen that the older respondents live alone, and if this occurrence is common, then there can be numerous more survey questions which can help researchers try to understand what happens as time goes on that makes individuals want to live alone, if that is actually a phenomenon that happens. 
   
    

## Appendix


Here is a sample of 6 case ID's. I have fitted them into the page, please zoom  into the page to see the writing with more clarity. 

Appendix,  Figure 1
```{r}
show<- as.data.frame(head(newdata[,1:7]))
#knitr::kable(show) %>%
#  column_spec(1, width = "10em")%>%
#  kable_styling(font_size = 7)

kable((show), format="latex", booktabs=TRUE) %>% 
  kable_styling(latex_options="scale_down")

show2<- as.data.frame(head(newdata[,8:14]))

kable((show2), format="latex", booktabs=TRUE) %>% 
  kable_styling(latex_options="scale_down")

show3<- as.data.frame(head(newdata[,15:21]))

kable((show3), format="latex", booktabs=TRUE) %>% 
  kable_styling(latex_options="scale_down")

show4<- as.data.frame(head(newdata[,22:29]))

kable((show4), format="latex", booktabs=TRUE) %>% 
  kable_styling(latex_options="scale_down")

show5<- as.data.frame(head(newdata[,30:37]))

kable((show5), format="latex", booktabs=TRUE) %>% 
  kable_styling(latex_options="scale_down")

show6<- as.data.frame(head(newdata[,38:45]))

kable((show6), format="latex", booktabs=TRUE) %>% 
  kable_styling(latex_options="scale_down")

show7<- as.data.frame(head(newdata[,46:50]))

kable((show7), format="latex", booktabs=TRUE) %>% 
  kable_styling(latex_options="scale_down")

#kable((show), format="latex", booktabs=TRUE) %>% 
#  kable_styling(latex_options="scale_down")

```

## Missing Values
Here are the percentages of missing values per predictor in  the dataset. I removed variables with >55% missing values. 

```{r, echo=FALSE}
missdata <- read.csv("gss.csv")
#is.na(missdata)
#colSums(is.na(missdata))
((colSums(is.na(missdata)))/20602)*100

```



## References

- Holt-Lunstad, Julianne. “The Double Pandemic Of Social Isolation And COVID-19: Cross-Sector Policy Must Address Both.” The Double Pandemic Of Social Isolation And COVID-19: Cross-Sector Policy Must Address Both | Health Affairs, 22 June 2020, www.healthaffairs.org/do/10.1377/hblog20200609.53823.

- Government of Canada, Statistics Canada. “Canada at a Glance 2018 Population.” Population - Canada at a Glance, 2018, Statistics Canada, 27 Mar. 2018, www150.statcan.gc.ca/n1/pub/12-581-x/2018000/pop-eng.htm.

- “General Social Survey: An Overview, 2019.” Statistics Canada: Canada's National Statistical Agency, Government of Canada, 20 Feb. 2019, www150.statcan.gc.ca/n1/pub/89f0115x/89f0115x2019001-eng.htm.


- Government of Canada, Statistics Canada. “General Social Survey - Family (GSS).” Surveys and Statistical Programs, 6 Feb. 2019, www23.statcan.gc.ca/imdb/p2SV.pl?Function=getSurvey&SDDS=4501.

- Statistics Canada.  (April 2020). Volume Number: 2019001.  -General Social Survey, Cycle 31: Families. Public use Microdata File Documentation and user's guide. CHASS Data Centre. Retrieved from https://sda-artsci-utoronto-ca.myaccess.library.utoronto.ca/sdaweb/dli2/gss/gss31/gss31/more_doc/GSS31_User_Guide.pdf

- Statistics Canada-CHASS Data Centre.-General Social Survey, Cycle 31: Families Dataset (2017).Retrieved from 
https://sda-artsci-utoronto-ca.myaccess.library.utoronto.ca/cgi-bin/sda/subsda3

- R Core Team (2020). R: A language and environment for statistical computing. R, Foundation for Statistical Computing, Vienna, Austria. URL, https://www.R-project.org/.

- JJ Allaire and Yihui Xie and Jonathan McPherson and Javier Luraschi and Kevin Ushey and Aron Atkins and Hadley Wickham and Joe Cheng and Winston Chang and Richard Iannone (2020). rmarkdown: Dynamic Documents for R. R package version 2.3. URL https://rmarkdown.rstudio.com.

- Wickham et al., (2019). Welcome to the tidyverse. Journal of Open Source
  Software, 4(43), 1686, https://doi.org/10.21105/joss.01686
  
- Venables, W. N. & Ripley, B. D. (2002) Modern Applied Statistics with S.
  Fourth Edition. Springer, New York. ISBN 0-387-95457-0
  
- Frank E Harrell Jr (2020). rms: Regression Modeling Strategies. R package
  version 6.0-1. https://CRAN.R-project.org/package=rms

-  Hadley Wickham, Romain François, Lionel Henry and Kirill Müller (2020).
  dplyr: A Grammar of Data Manipulation. R package version 1.0.2.
  https://CRAN.R-project.org/package=dplyr
  
- Jerome Friedman, Trevor Hastie, Robert Tibshirani (2010). Regularization
  Paths for Generalized Linear Models via Coordinate Descent. Journal of
  Statistical Software, 33(1), 1-22. URL http://www.jstatsoft.org/v33/i01/.
 
- H. Wickham. ggplot2: Elegant Graphics for Data Analysis. Springer-Verlag
  New York, 2016.

- Baptiste Auguie (2017). gridExtra: Miscellaneous Functions for "Grid"
  Graphics. R package version 2.3.
  https://CRAN.R-project.org/package=gridExtra
  
- Matthijs Meire, Michel Ballings and Dirk Van den Poel (2016).
  imputeMissings: Impute Missing Values in a Predictive Context. R package
  version 0.0.3. https://CRAN.R-project.org/package=imputeMissings

- Kirill Müller, Hadley Wickham, David A. James and Seth Falcon (2020).
  RSQLite: 'SQLite' Interface for R. R package version 2.2.1.
  https://CRAN.R-project.org/package=RSQLite
  
- Hao Zhu (2020). kableExtra: Construct Complex Table with 'kable' and Pipe
  Syntax. R package version 1.2.1.
  https://CRAN.R-project.org/package=kableExtra
  

- Daniel D. Sjoberg, Michael Curry, Margie Hannum, Karissa Whiting and
  Emily C. Zabor (2020). gtsummary: Presentation-Ready Data Summary and
  Analytic Result Tables. R package version 1.3.5.
  https://CRAN.R-project.org/package=gtsummary
 
- T. Lumley (2020) "survey: analysis of complex survey samples". R package
  version 4.0.
  
- Rohan Alexander, Sam Caetano. "GSS_cleaning.R","gss_dict.txt", "gss_labels.txt". October 2020. Retrieved from https://q.utoronto.ca/courses/184060/modules. 

  



